%!TEX root = ../Thesis.tex

\chapter{Schedule}
\textit{TODO: Obviously this won't be in the final version :-)}
This chapter describes a rough planning for the full thesis project. It is hard to foresee the time required for the individual goals of the project which makes it likely that time lines will shift.

\bigskip
\bigskip

\begin{longtable}{r|p{9cm}}
 December-January & Proposal, background study \\
 &\footnotesize{Kicking off the project, writing the project proposal. Final version by January.}\\\multicolumn{2}{c}{} \\
 
 January & Framework, explorative experiments, write background \\
 &\footnotesize{Create environment for testing and running experiments. Finish background chapter for thesis, detailing the inner working of JPEG, overview of artifacts, and existing (non-deep learning) approaches for artifact removal (5 to 7 pages?).}\\\multicolumn{2}{c}{} \\
 
February & Gather datasets, implement architectures\\
&\footnotesize{Collect datasets to evaluate the project's system. If feeling ambitious, also generate random vector images. Apply the network architectures described in section 2.1, as well as tweaking their hyperparameters. Aside from tweaking the parameters, different pre and postprocessing methods such as data augmentation will be explored to further increase the performance of the networks. Finish methods chapter of thesis (\~5 pages?).}\\\multicolumn{2}{c}{} \\
 
  March- & Further tweaking, evaluate different initialization and sampling strategies \\
 March&\footnotesize{Proper initialization is very important for this problem. Evaluate some different initialization strategies as described in literature, and continue tweaking architectures. Collect first results and describe these. Create shell for results chapter (around 3 pages?)   }\\\multicolumn{2}{c}{} \\
 
   Early April & Run final experiments, gather and describe results. \\\multicolumn{2}{c}{} \\
 
    April & Buffer and finalizing the thesis \\
 &\footnotesize{Buffer for previous steps, room for stretch goals, writing the final version of the thesis. Late April or start of May: thesis presentation and defense, concluding the project.}\\\multicolumn{2}{c}{} \\
\end{longtable}
